---
title: "Lecture4.1_Assignment_Student"
author: "Zhuo Qu"
date: "2025-07-02"
output: html_document
---

```{r setup, include=FALSE}
```

Please complete the following problems. For each counting part, clearly state which of the **four scenarios** (With/Without Replacement, Order Matters/Doesn't Matter) applies. You may use R for calculations.

**Problem 1: The Code Creation  <span class="highlight-point">(4 Pts)</span>**

   a) How many 5-character codes can be formed using distinct uppercase letters (A-Z, 26 letters) if the order matters? (Scenario?)
```{r assignment 1a}
code_a <- NA ## How many 5-character codes can be formed using distinct uppercase letters (A-Z, 26 letters) if the order matters
```
   b) How many 5-character codes can be formed using uppercase letters (A-Z) if letters can be repeated and order matters? (Scenario?)
```{r assignment 1b}
code_b <- NA ## How many 5-character codes can be formed using uppercase letters (A-Z) if letters can be repeated and order matters

```
   
   c) How many ways can you select a group of 5 distinct letters from the alphabet if the order of selection does not matter? (Scenario?)
```{r assignment 1c}
code_c <- NA ## How many ways can you select a group of 5 distinct letters from the alphabet if the order of selection does not matter?
```   
   d) How many ways can you choose 5 letters from the alphabet if repetition is allowed but the order of the chosen letters does not matter (e.g., AABBC is the same as BABCA as a final collection)? (Scenario?)
   
 Problem 1 Answer (Only shown to lecturer's version)
```{r assignment 1d}

code_d <- NA ## How many ways can you choose 5 letters from the alphabet if repetition is allowed but the order of the chosen letters does not matter (e.g., AABBC is the same as BABCA as a final collection)? (Scenario?)
```
   

**Problem 2: The Candy Store  <span class="highlight-point">(3 Pts)</span>**

A candy store sells 10 different types of gummy candies. You want to buy a bag of 6 gummy candies.

   a) If you pick 6 *different* types of gummy candies and the order you picked them is noted by the clerk, how many ways can this be done? (Scenario?)
   
```{r assignment 2a}
candy_a <- NA ## If you pick 6 *different* types of gummy candies and the order you picked them is noted by the clerk, how many ways can this be done
```
   
   b) If you pick 6 *different* types of gummy candies and the collection of 6 is all that matters, how many ways? (Scenario?)
   
```{r assignment 2b}
candy_b <- NA ## If you pick 6 *different* types of gummy candies and the collection of 6 is all that matters, how many ways?
```
   c) If you can pick multiples of the same type of gummy candy and the final collection of 6 is all that matters (e.g., 3 of type A, 2 of type B, 1 of type C), how many ways? (Scenario?)

 Problem 2 Answer (Only shown to lecturer's version)   
```{r assignment 2c}
candy_c <- NA ## If you can pick multiples of the same type of gummy candy and the final collection of 6 is all that matters (e.g., 3 of type A, 2 of type B, 1 of type C), how many ways?
```

**Problem 3: The Card Game (Probability <span class="highlight-point">(4 Pts)</span>)**

You are dealt a hand of 5 cards from a standard 52-card deck.

   a) How many total possible 5-card hands are there? (Scenario?) <span class="highlight-point">(1 Pt)</span>
```{r assignment 3a}
total_hands <- NA ## How many total possible 5-card hands are there
```
   b) How many hands contain exactly 2 Kings and exactly 2 Queens? (Hint: You'll also need to choose one more card that is not a King or Queen). <span class="highlight-point">(1 Pt)</span>
```{r assignment 3b}
kings <- NA ## How many selections of 2 Kings out of four Kings?
queens <- NA ## How many selections of 2 Queens out of four Queens?
other_cards <- NA ## How many options of choosing 1 remaining card from non-King and non-Queen cards?
favorable_b <- NA ## How many hands contain exactly 2 Kings and exactly 2 Queens?
```   
   c) What is the probability of being dealt a hand with exactly 2 Kings and 2 Queens? <span class="highlight-point">(1 Pt)</span>
```{r assignment 3c}
prob_c <- NA ## What is the probability of being dealt a hand with exactly 2 Kings and 2 Queens
```   
   d) What is the probability of having no Kings and no Queens? <span class="highlight-point">(1 Pt)</span>
   
 Problem 3 Answer (Only shown to lecturer's version)   
```{r assignment 3d}
no_qk <- NA ## hands of no Kings and Queens among 5 cards
prob_d <- NA ## What is the probability of having no Kings and no Queens?
```

**Problem 4: The Texas Hold'em Poker Game <span class="highlight-point">(10 Pts)</span>**

In Texas Hold'em poker, players receive 5-card hands from a standard 52-card deck. Calculate the probabilities (as percentages) and odds against (in x : 1 format) for these hand types, ordered from most to least likely. Odds are defined as probability/(1-Probability), meaning odds failures for every 1 success. *(1 Pt per sub-question)*

 a) **No Pair (High Card) <span class="highlight-point">(1 Pt)</span>**
Hand with no matching ranks, *no 5-card sequence*, and not all same suit.
Example: A♠ K♦ 10♣ 7♥ 4♠

```{r assignment 4a}
total_hands <- NA ## Total selection of one hand (five cards from 52-cards, without replacement, order does not matter)
high_card <- NA ## Total selection of high card
prob_high_card <- NA ## Probability of high card
odds_high_card <- NA ## Odds of high card
```
b) **One Pair <span class="highlight-point">(1 Pt)</span>**
Exactly two matching-rank cards + three unmatched-rank cards.
Example: 10♠ 10♥ 3♦ Q♣ K♠
```{r assignment 4b}
one_pair <- NA
prob_one_pair <- NA
odds_one_pair <- NA
```
c) **Two Pair <span class="highlight-point">(1 Pt)</span>**
Two different pairs (two cards each of two ranks) + one unmatched card.
Example: 9♥ 9♦ K♣ K♠ 4♥
```{r assignment 4c}
two_pairs <- NA
prob_two_pairs <- NA
odds_two_pairs <- NA
```
d) **Three of a Kind <span class="highlight-point">(1 Pt)</span>**
Exactly three matching-rank cards + two differing unmatched-rank cards.
Example: 7♠ 7♥ 7♦ 4♣ 5♠
```{r assignment 4d}
three_kind <- NA
prob_three_kind <- NA
odds_three_kind <- NA
```
e) **Straight (excl. straight/royal flush) <span class="highlight-point">(1 Pt)</span>**
Five sequentially ranked cards (e.g., 7-8-9-10-J or A-2-3-4-5), not all same suit.
Example: A♥ 2♣ 3♠ 4♥ 5♠ (Ace-low)
```{r assignment 4e}
straight <- NA
prob_straight <- NA
odds_straight <- NA
```
f) **Flush (excl. straight/royal flush) <span class="highlight-point">(1 Pt)</span>**
Five same-suit cards, not in sequence.
Example: 2♥ 4♥ 5♥ 9♥ K♥ (hearts)
```{r assignment 4f}
flush <- NA
prob_flush <- NA
odds_flush <- NA
```
g) **Full House <span class="highlight-point">(1 Pt)</span>**
Three cards of one rank + two cards of another rank.
Example: J♥ J♦ J♠ K♣ K♠ (Jacks full of Kings)
```{r assignment 4g}
full_house <- NA
prob_full_house <- NA
odds_full_house <- NA
```
h) **Four of a Kind <span class="highlight-point">(1 Pt)</span>**
Four matching-rank cards + one any other rank card.
Example: 3♠ 3♥ 3♦ 3♣ 4♥ (fours threes)
```{r assignment 4h}
four_kind <- NA
prob_four_kind <- NA
odds_four_kind <- NA
```
i) **Straight Flush (excl. royal flush) <span class="highlight-point">(1 Pt)</span>**
Five sequentially ranked same-suit cards, not Ace-high.
Example: 5♥ 6♥ 7♥ 8♥ 9♥ (hearts)
```{r assignment 4i}
straight_flush <- NA
prob_straight_flush <- NA
odds_straight_flush <- NA
```
j) **Royal Flush <span class="highlight-point">(1 Pt)</span>**
Ace, King, Queen, Jack, Ten all same suit.
Example: 10♦ J♦ Q♦ K♦ A♦ (diamonds)

Problem 4 Answer (Only shown to lecturer's version)

```{r assignment4j}
royal_flush <- NA
prob_royal_flush <- NA
odds_royal_flush <- NA
```

```{r assignment4}
## Summary of the above probability and odds of hands in Texas Holdem
# Hand type counts from poker combinatorics
hands <- c(
  "High Card" = high_card,
  "One Pair" = one_pair,
  "Two Pair" = two_pairs,
  "Three of a Kind" = three_kind,
  "Straight" = straight,
  "Flush" = flush,
  "Full House" = full_house,
  "Four of a Kind" = four_kind,
  "Straight Flush" = straight_flush,
  "Royal Flush" = royal_flush
)

# Create results table
results <- data.frame(
  Hand = names(hands),
  Count = hands,
  Probability = round(hands / total_hands * 100, 2),
  Odds_Against = round((total_hands - hands) / hands, 1)
)

# Print full table
print(results)


```
